---
title: "BC Stats Web Traffic Monitoring"
logo: "www/bcstats_logo_rev.png"
format: 
  dashboard:
    theme:
      - litera
      - theme.scss
    orientation: rows
    embed-resources: true
    nav-buttons:
      - icon: github
        href: https://github.com/bcgov/bcstats-webtraffic-monitoring
---

<!-- 
HOW TO RUN THIS DASHBOARD FOR CODE REVIEW:
Option 1: In Positron or RStudio, open this file and click the "Render" button at the top.
Option 2: Run the following in the R Console: `quarto::quarto_render("Report/gdx_web_dashboard.qmd")`
Option 3: Run the following in the Terminal: `quarto preview Report/gdx_web_dashboard.qmd`

Data is produced by R/gdx-02-analyze.R, which writes the cmslite_*.csv
tables to OUTPUT_TABLES.
-->

```{r setup, include=FALSE}
library(readr)
library(dplyr)
library(purrr)
library(knitr)
library(ggplot2)
library(forcats)
library(plotly)
library(lubridate)
library(safepaths)
library(glue)
library(DT)
library(scales)
library(crosstalk)
library(htmltools)

`%||%` <- function(a, b) if (is.null(a)) b else a

# Resolve OUTPUT_TABLES the same way 00-setup.R does.
LAN_FOLDER <- use_network_path()
PROJECT_ROOT <- glue("{LAN_FOLDER}/0. Misc/Data Science Tooling/web-hosting-and-dashboards/shinyapps_webtraffic_monitoring")
OUTPUT_TABLES <- glue("{PROJECT_ROOT}/outputs/tables")

# Read month-partitioned CMS Lite summary tables if they exist; otherwise fall
# back to the legacy flat files so older outputs still render.
cmslite_root <- file.path(OUTPUT_TABLES, "cms_lite")
cmslite_months <- if (dir.exists(cmslite_root)) {
  sort(list.dirs(cmslite_root, recursive = FALSE, full.names = FALSE))
} else {
  character()
}

# Optional cap so a historical render reflects what was known as of that month.
# Without it the dashboard always treats the newest month on disk as current,
# which would make a backfilled July render headline August.
dashboard_max_month <- Sys.getenv("GDX_DASHBOARD_MAX_MONTH", unset = "")
if (nzchar(dashboard_max_month) && length(cmslite_months) > 0) {
  kept <- cmslite_months[cmslite_months <= dashboard_max_month]
  if (length(kept) == 0) {
    stop(
      sprintf(
        "GDX_DASHBOARD_MAX_MONTH=%s excludes every available month (%s).",
        dashboard_max_month,
        paste(cmslite_months, collapse = ", ")
      ),
      call. = FALSE
    )
  }
  cmslite_months <- kept
}

cmslite_month_label <- function(month) {
  format(as.Date(paste0(month, "-01")), "%B %Y")
}

read_cmslite_month <- function(name, month) {
  path <- file.path(cmslite_root, month, sprintf("%s_%s.csv", name, month))
  if (file.exists(path)) {
    read_csv(path, show_col_types = FALSE)
  } else {
    NULL
  }
}

read_cmslite_legacy <- function(name) {
  path <- file.path(OUTPUT_TABLES, paste0(name, ".csv"))
  if (file.exists(path)) {
    read_csv(path, show_col_types = FALSE)
  } else {
    NULL
  }
}

load_cmslite_monthly <- function(name) {
  if (length(cmslite_months) > 0) {
    out <- map(cmslite_months, \(m) read_cmslite_month(name, m))
    names(out) <- cmslite_months
    out[!map_lgl(out, is.null)]
  } else {
    legacy <- read_cmslite_legacy(name)
    if (is.null(legacy)) list() else list(legacy = legacy)
  }
}

bind_cmslite_monthly <- function(name) {
  tbls <- load_cmslite_monthly(name)
  if (length(tbls) == 0) {
    return(NULL)
  }

  list_rbind(
    imap(tbls, \(x, month) dplyr::mutate(x, month = month, month_label = cmslite_month_label(month), .before = 1))
  )
}

month_site_dropdown_barh <- function(data, label_col, value_col, value_name,
                                     title_prefix, top_n = 15, pre_aggregate = FALSE) {
  month_list <- sort(unique(data$month))
  site_list <- sort(unique(data$site))
  has_full <- "full_label" %in% names(data)

  prep_combo <- function(m, s) {
    d <- data |> filter(month == m, site == s)
    if (pre_aggregate) {
      group_cols <- if (has_full) c(label_col, "full_label") else label_col
      d <- d |>
        summarize(
          !!value_col := sum(.data[[value_col]], na.rm = TRUE),
          .by = all_of(group_cols)
        )
    }
    d |>
      arrange(desc(.data[[value_col]])) |>
      slice_head(n = top_n) |>
      # Plotly horizontal bars render first row at the bottom; keep ascending
      # order in traces so highest value appears at the top.
      arrange(.data[[value_col]])
  }

  combos <- expand.grid(month = month_list, site = site_list, stringsAsFactors = FALSE)
  data_by_combo <- map2(combos$month, combos$site, prep_combo)
  combo_names <- paste(combos$month, combos$site, sep = "__")
  names(data_by_combo) <- combo_names

  default_month <- month_list[length(month_list)]
  default_site <- site_list[1]
  default_name <- paste(default_month, default_site, sep = "__")

  p <- plot_ly()
  for (nm in combo_names) {
    d <- data_by_combo[[nm]]
    p <- add_bars(
      p,
      x = d[[value_col]],
      y = d[[label_col]],
      orientation = "h",
      visible = nm == default_name,
      marker = list(color = "#2F6B3F", line = list(color = "white", width = 0.5), opacity = 0.9),
      customdata = if (has_full) d$full_label else d[[label_col]],
      hovertemplate = paste0("<b>%{customdata}</b><br>", value_name, ": %{x:,}<extra></extra>"),
      showlegend = FALSE
    )
  }

  month_buttons <- lapply(month_list, function(m) {
    vis <- map_lgl(combo_names, ~startsWith(.x, paste0(m, "__")))
    d <- data_by_combo[[paste(m, default_site, sep = "__")]]
    list(
      method = "update",
      args = list(
        list(visible = as.list(vis)),
        list(
          title = list(
            text = paste0("<b>", title_prefix, " – ", cmslite_month_label(m), "</b>"),
            font = modifyList(bc_font, list(size = 15, color = "#003366"))
          ),
          yaxis = list(
            title = "", automargin = TRUE,
            tickfont = modifyList(bc_font, list(size = 10, color = "#2d2d2d"))
          )
        )
      ),
      label = cmslite_month_label(m)
    )
  })

  site_buttons <- lapply(site_list, function(s) {
    vis <- map_lgl(combo_names, ~endsWith(.x, paste0("__", s)))
    d <- data_by_combo[[paste(default_month, s, sep = "__")]]
    list(
      method = "update",
      args = list(
        list(visible = as.list(vis)),
        list(
          title = list(
            text = paste0("<b>", title_prefix, " – ", site_short(s), "</b>"),
            font = modifyList(bc_font, list(size = 15, color = "#003366"))
          ),
          yaxis = list(
            title = "", automargin = TRUE,
            tickfont = modifyList(bc_font, list(size = 10, color = "#2d2d2d"))
          )
        )
      ),
      label = site_short(s)
    )
  })

  default_d <- data_by_combo[[default_name]]

  p |>
    layout(
      title = list(
        text = paste0("<b>", title_prefix, " – ", cmslite_month_label(default_month), "</b>"),
        font = modifyList(bc_font, list(size = 15, color = "#003366"))
      ),
      xaxis = list(title = "", gridcolor = "#e8ecf0", zeroline = FALSE,
                   tickfont = modifyList(bc_font, list(size = 10, color = "#5c6b7a"))),
      yaxis = list(title = "", automargin = TRUE,
                   tickfont = modifyList(bc_font, list(size = 10, color = "#2d2d2d")),
                   categoryorder = "trace"),
      updatemenus = list(
        list(
          type = "dropdown", direction = "down",
          x = 0.0, xanchor = "left", y = 1.36, yanchor = "top",
          buttons = month_buttons,
          active = length(month_list) - 1L,
          showactive = TRUE, bgcolor = "#f5f8fb", bordercolor = "#c8d8e8",
          font = modifyList(bc_font, list(size = 11))
        ),
        list(
          type = "dropdown", direction = "down",
          x = 0.32, xanchor = "left", y = 1.36, yanchor = "top",
          buttons = site_buttons,
          active = 0L,
          showactive = TRUE, bgcolor = "#f5f8fb", bordercolor = "#c8d8e8",
          font = modifyList(bc_font, list(size = 11))
        )
      ),
      plot_bgcolor = "#ffffff", paper_bgcolor = "#ffffff",
      margin = list(l = 10, r = 30, t = 115, b = 30), bargap = 0.3
    ) |>
    config(
      displaylogo = plotly_config$displaylogo,
      modeBarButtonsToRemove = plotly_config$modeBarButtonsToRemove,
      responsive = plotly_config$responsive
    )
}

daily_by_month <- load_cmslite_monthly("cmslite_daily")
top_pages_by_month <- load_cmslite_monthly("cmslite_top_pages")
clicks_daily_by_month <- load_cmslite_monthly("cmslite_clicks_daily")
top_targets_by_month <- load_cmslite_monthly("cmslite_top_targets")
top_referrers_by_month <- load_cmslite_monthly("cmslite_top_referrers")
by_os_by_month <- load_cmslite_monthly("cmslite_by_os")
by_geo_by_month <- load_cmslite_monthly("cmslite_by_geo")
asset_daily_by_month <- load_cmslite_monthly("cmslite_asset_downloads_daily")
top_assets_by_month <- load_cmslite_monthly("cmslite_top_assets")
search_terms_by_month <- load_cmslite_monthly("cmslite_search_terms")
google_queries_by_month <- load_cmslite_monthly("cmslite_google_queries")

daily          <- bind_cmslite_monthly("cmslite_daily")
top_pages      <- bind_cmslite_monthly("cmslite_top_pages")
clicks_daily   <- bind_cmslite_monthly("cmslite_clicks_daily")
top_targets    <- bind_cmslite_monthly("cmslite_top_targets")
top_referrers  <- bind_cmslite_monthly("cmslite_top_referrers")
by_os          <- bind_cmslite_monthly("cmslite_by_os")
by_geo         <- bind_cmslite_monthly("cmslite_by_geo")
asset_daily    <- bind_cmslite_monthly("cmslite_asset_downloads_daily")
top_assets     <- bind_cmslite_monthly("cmslite_top_assets")
search_terms   <- bind_cmslite_monthly("cmslite_search_terms")
google_queries <- bind_cmslite_monthly("cmslite_google_queries")

# Sites present in the data (data-driven).
sites <- sort(unique(daily$site))

# Use discovered month partitions as the source of truth.
months_available <- names(daily_by_month)
cmslite_months <- sort(months_available)
current_month <- if (length(cmslite_months) > 0) tail(cmslite_months, 1) else NA_character_
previous_month <- if (length(cmslite_months) > 1) cmslite_months[length(cmslite_months) - 1] else NA_character_
current_month_str <- if (!is.na(current_month)) cmslite_month_label(current_month) else ""
previous_month_str <- if (!is.na(previous_month)) cmslite_month_label(previous_month) else NA_character_

# Proper web-property names. coalesce() keeps unknown sites working.
site_label_map <- c(
  all_sites  = "All Sites",
  outcomes   = "Student Outcomes",
  antiracism = "Anti-Racism Data Act",
  govstats   = "BC Stats"
)
site_label <- function(s) coalesce(unname(site_label_map[s]), s)

site_short_map <- c(
  all_sites  = "All Sites",
  outcomes   = "Student Outcomes",
  antiracism = "Anti-Racism Data Act",
  govstats   = "BC Stats"
)
site_short <- function(s) coalesce(unname(site_short_map[s]), s)

# Underlying CMS platform per property (BC Stats is CMS Lite; the two bcstats
# survey properties are WordPress sites).
site_platform_map <- c(
  outcomes   = "WordPress",
  antiracism = "WordPress",
  govstats   = "CMS Lite"
)
site_platform <- function(s) coalesce(unname(site_platform_map[s]), "")

# BC-blue family palette, keyed by site, with grey fallback.
site_palette_pool <- c("#003366", "#1F6B75", "#9E4C1A", "#6C3D8A", "#2F6B3F", "#B07D12")
site_colors <- setNames(
  site_palette_pool[seq_along(sites)],
  sites
)
site_colors[is.na(site_colors)] <- "#888888"

# Date range covered by the data (used in titles/subtitles).
date_min <- min(daily$date, na.rm = TRUE)
date_max <- max(daily$date, na.rm = TRUE)
date_range_str <- if (format(date_min, "%Y-%m") == format(date_max, "%Y-%m")) {
  format(date_min, "%B %Y")
} else {
  paste0(format(date_min, "%b %d, %Y"), " \u2013 ", format(date_max, "%b %d, %Y"))
}

# Sum a metric for a given month from month-partitioned list input.
# Returns NA when that month or metric is absent.
month_total <- function(monthly_tbls, value_col, month) {
  if (is.null(monthly_tbls) || length(monthly_tbls) == 0 || is.na(month)) {
    return(NA_real_)
  }
  d <- monthly_tbls[[month]]
  if (is.null(d) || !value_col %in% names(d)) {
    return(NA_real_)
  }
  sum(d[[value_col]], na.rm = TRUE)
}

# Build a "+/-% vs <label>" caption; empty string when the comparison is missing.
delta_caption <- function(current, comparison, label) {
  if (is.na(comparison) || comparison == 0 || is.na(current)) return("")
  pct <- (current - comparison) / comparison
  arrow <- if (pct >= 0) "\u25B2" else "\u25BC"
  sprintf(" (%s%s vs %s)", arrow, percent(abs(pct), accuracy = 0.1), label)
}

# This-month totals across all sites (for value boxes).
total_page_views <- month_total(daily_by_month, "page_views", current_month)
total_sessions   <- month_total(daily_by_month, "sessions", current_month)
total_clicks     <- month_total(clicks_daily_by_month, "clicks", current_month)

previous_page_views <- month_total(daily_by_month, "page_views", previous_month)
previous_sessions   <- month_total(daily_by_month, "sessions", previous_month)
previous_clicks     <- month_total(clicks_daily_by_month, "clicks", previous_month)

# Month-over-month delta captions (empty until multi-month data exists).
pv_delta          <- delta_caption(total_page_views, previous_page_views, previous_month_str)
sessions_delta    <- delta_caption(total_sessions, previous_sessions, previous_month_str)
clicks_delta      <- delta_caption(total_clicks, previous_clicks, previous_month_str)

# Engagement: page views per session (avoids the daily-unique over-count of users).
pv_per_session <- if (!is.na(total_sessions) && total_sessions > 0) total_page_views / total_sessions else NA_real_
previous_pv_per_session <- if (!is.na(previous_sessions) && previous_sessions > 0) previous_page_views / previous_sessions else NA_real_
pv_per_session_delta <- delta_caption(pv_per_session, previous_pv_per_session, previous_month_str)

# Shared Plotly branding helpers (match shinyapps_dashboard.qmd).
bc_font <- list(family = "BC Sans, Segoe UI, Arial, sans-serif")

plotly_config <- list(
  displaylogo = FALSE,
  modeBarButtonsToRemove = list(
    "zoom2d", "pan2d", "select2d", "lasso2d",
    "zoomIn2d", "zoomOut2d", "autoScale2d",
    "hoverClosestCartesian", "hoverCompareCartesian"
  ),
  responsive = TRUE
)

# Shorten a long display URL for axis labels; full value kept for hover.
# Intentionally used only by the Top Downloaded Assets chart now; the page,
# referrer, and location charts display full labels.
shorten_url <- function(x, max_chars = 55) {
  x <- ifelse(is.na(x) | x == "" | x == "(not set)", "(unknown)", x)
  # Drop scheme + host so the path stands out.
  stripped <- sub("^https?://[^/]+", "", x)
  stripped <- ifelse(stripped == "" | stripped == "/", x, stripped)
  ifelse(
    nchar(stripped) > max_chars,
    paste0("\u2026", substr(stripped, nchar(stripped) - max_chars + 1, nchar(stripped))),
    stripped
  )
}

# Build a horizontal bar chart with a per-site dropdown (one trace per site).
# `data` must have columns: site, <label_col>, <value_col>, and optionally
# `full_label` (used for hover; falls back to <label_col>).
# When `pre_aggregate = TRUE`, values are summed by label within each site before
# ranking (e.g. region/country rows that repeat within a site).
# Ordering is enforced per site via yaxis categoryarray so the largest value is
# always at the top, including after switching sites via the dropdown.
site_dropdown_barh <- function(data, label_col, value_col, value_name,
                               title_prefix, top_n = 15, pre_aggregate = FALSE,
                               show_dropdown = TRUE, include_all_sites = FALSE,
                               default_site = NULL) {
  site_list <- sort(unique(data$site))

  # With a single source there is nothing to switch between, so suppress the
  # dropdown and render a plain titled bar chart.
  if (length(site_list) <= 1 && !include_all_sites) show_dropdown <- FALSE

  has_full <- "full_label" %in% names(data)

  prep_site <- function(s) {
    is_all_sites <- identical(s, "all_sites")
    d <- if (is_all_sites) data else data |> filter(site == s)

    # Always aggregate duplicate labels for the All Sites view. Otherwise
    # identical labels from different sites can show as separate bars.
    if (pre_aggregate || is_all_sites) {
      group_cols <- if (has_full) c(label_col, "full_label") else label_col
      d <- d |>
        summarize(
          !!value_col := sum(.data[[value_col]], na.rm = TRUE),
          .by = all_of(group_cols)
        )
    }

    d |>
      arrange(desc(.data[[value_col]])) |>
      slice_head(n = top_n) |>
      # Plotly horizontal bars render first row at the bottom; keep ascending
      # order in traces so highest value appears at the top.
      arrange(.data[[value_col]])
  }

  plot_sites <- if (include_all_sites) c("all_sites", site_list) else site_list
  data_by_site <- lapply(plot_sites, prep_site)
  names(data_by_site) <- plot_sites

  if (is.null(default_site)) {
    default_site <- if (include_all_sites) {
      "all_sites"
    } else {
      data |>
        summarize(v = sum(.data[[value_col]], na.rm = TRUE), .by = site) |>
        slice_max(v, n = 1) |>
        pull(site)
    }
  }

  p <- plot_ly()
  for (s in plot_sites) {
    d <- data_by_site[[s]]
    marker_color <- if (identical(s, "all_sites")) "#003366" else unname(site_colors[s])
    p <- add_bars(
      p,
      x = d[[value_col]],
      y = d[[label_col]],
      orientation = "h",
      visible = s == default_site,
      marker = list(color = marker_color,
                    line = list(color = "white", width = 0.5), opacity = 0.9),
      customdata = if (has_full) d$full_label else d[[label_col]],
      hovertemplate = paste0("<b>%{customdata}</b><br>", value_name, ": %{x:,}<extra></extra>"),
      showlegend = FALSE
    )
  }

  buttons <- lapply(seq_along(plot_sites), function(i) {
    s <- plot_sites[i]
    d <- data_by_site[[s]]
    vis <- rep(FALSE, length(plot_sites))
    vis[i] <- TRUE
    list(
      method = "update",
      args = list(
        list(visible = as.list(vis)),
        list(
          title = list(
            text = paste0("<b>", title_prefix, " \u2013 ", site_short(s), "</b>"),
            font = modifyList(bc_font, list(size = 15, color = "#003366"))
          ),
          yaxis = list(
            title = "", automargin = TRUE,
            tickfont = modifyList(bc_font, list(size = 10, color = "#2d2d2d"))
          )
        )
      ),
      label = site_short(s)
    )
  })

  default_d <- data_by_site[[default_site]]

  updatemenus <- if (show_dropdown) {
    list(list(
      type = "dropdown", direction = "down",
      x = 0.0, xanchor = "left", y = 1.36, yanchor = "top",
      buttons = buttons,
      active = which(plot_sites == default_site) - 1L,
      showactive = TRUE, bgcolor = "#f5f8fb", bordercolor = "#c8d8e8",
      font = modifyList(bc_font, list(size = 11))
    ))
  } else {
    list()
  }

  # Trim top margin when there is no dropdown occupying vertical space.
  top_margin <- if (show_dropdown) 115 else 50

  p |>
    layout(
      title = list(
        text = paste0("<b>", title_prefix, if (show_dropdown) paste0(" \u2013 ", site_short(default_site)) else "", "</b>"),
        font = modifyList(bc_font, list(size = 15, color = "#003366"))
      ),
      xaxis = list(title = "", gridcolor = "#e8ecf0", zeroline = FALSE,
                   tickfont = modifyList(bc_font, list(size = 10, color = "#5c6b7a"))),
      yaxis = list(title = "", automargin = TRUE,
                   tickfont = modifyList(bc_font, list(size = 10, color = "#2d2d2d")),
                   categoryorder = "trace"),
      updatemenus = updatemenus,
      plot_bgcolor = "#ffffff", paper_bgcolor = "#ffffff",
      margin = list(l = 10, r = 30, t = top_margin, b = 30), bargap = 0.3
    ) |>
    config(
      displaylogo = plotly_config$displaylogo,
      modeBarButtonsToRemove = plotly_config$modeBarButtonsToRemove,
      responsive = plotly_config$responsive
    )
}

daily_site_dropdown_line <- function(data, value_col, value_name, title_prefix,
                                     include_all_sites = TRUE,
                                     default_site = if (include_all_sites) "all_sites" else NULL) {
  site_list <- sort(unique(data$site))
  plot_sites <- if (include_all_sites) c("all_sites", site_list) else site_list

  prep_site <- function(s) {
    d <- if (identical(s, "all_sites")) {
      data |>
        summarize(!!value_col := sum(.data[[value_col]], na.rm = TRUE), .by = date)
    } else {
      data |>
        filter(site == s) |>
        arrange(date)
    }
    d |>
      arrange(date)
  }

  data_by_site <- lapply(plot_sites, prep_site)
  names(data_by_site) <- plot_sites

  if (is.null(default_site)) {
    default_site <- plot_sites[1]
  }

  p <- plot_ly()
  for (s in plot_sites) {
    d <- data_by_site[[s]]
    line_color <- if (identical(s, "all_sites")) "#003366" else unname(site_colors[s])
    p <- add_trace(
      p,
      x = d$date, y = d[[value_col]], type = "scatter", mode = "lines",
      name = site_short(s),
      visible = s == default_site,
      line = list(color = line_color, width = 2),
      hovertemplate = paste0("<b>", site_short(s), "</b><br>%{x|%b %d, %Y}<br>", value_name, ": %{y:,}<extra></extra>")
    )
  }

  buttons <- lapply(seq_along(plot_sites), function(i) {
    s <- plot_sites[i]
    vis <- rep(FALSE, length(plot_sites))
    vis[i] <- TRUE
    list(
      method = "update",
      args = list(
        list(visible = as.list(vis)),
        list(
          title = list(
            text = paste0("<b>", title_prefix, " – ", site_short(s), "</b>"),
            font = modifyList(bc_font, list(size = 15, color = "#003366"))
          )
        )
      ),
      label = site_short(s)
    )
  })

  p |>
    layout(
      title = list(
        text = paste0("<b>", title_prefix, " – ", site_short(default_site), "</b>"),
        font = modifyList(bc_font, list(size = 15, color = "#003366"))
      ),
      xaxis = list(title = "", gridcolor = "#e8ecf0", tickformat = "%b %d",
                   tickfont = modifyList(bc_font, list(size = 11, color = "#2d2d2d"))),
      yaxis = list(title = "", gridcolor = "#e8ecf0", automargin = TRUE,
                   tickfont = modifyList(bc_font, list(size = 11, color = "#5c6b7a"))),
      updatemenus = list(list(
        type = "dropdown", direction = "down",
        x = 0.0, xanchor = "left", y = 1.36, yanchor = "top",
        buttons = buttons,
        active = which(plot_sites == default_site) - 1L,
        showactive = TRUE, bgcolor = "#f5f8fb", bordercolor = "#c8d8e8",
        font = modifyList(bc_font, list(size = 11))
      )),
      plot_bgcolor = "#ffffff", paper_bgcolor = "#ffffff",
      margin = list(l = 10, r = 20, t = 115, b = 50)
    ) |>
    config(
      displaylogo = plotly_config$displaylogo,
      modeBarButtonsToRemove = plotly_config$modeBarButtonsToRemove,
      responsive = plotly_config$responsive
    )
}

```

# Summary {scrolling="true"}

## Row {height=210px}

::: {.valuebox color="primary" title="Page Views in `r current_month_str``r pv_delta`"}
`r comma(total_page_views)`
:::

::: {.valuebox color="info" title="Sessions in `r current_month_str``r sessions_delta`"}
`r comma(total_sessions)`
:::

::: {.valuebox color="secondary" title="Page Views per Session in `r current_month_str``r pv_per_session_delta`"}
`r formatC(pv_per_session, format = "f", digits = 2)`
:::

::: {.valuebox color="success" title="Clicks in `r current_month_str``r clicks_delta`"}
`r comma(total_clicks)`
:::

<!-- ::: {.callout-note appearance="minimal" collapse="true"}
Value boxes show totals for the latest month across all three properties.
Month-over-month change (▲/▼ %) appears automatically once more than one month of
data is available.
::: -->

## Row {height=500px}

### Daily Page Views by Site

```{r}
daily_site_dropdown_line(
  daily,
  value_col = "page_views",
  value_name = "Page views",
  title_prefix = paste0("Daily Page Views (", date_range_str, ")"),
  include_all_sites = TRUE,
  default_site = "all_sites"
)
```

## Row {height=520px}

### Daily Page Views by Site

```{r}
top_pages_plot <- top_pages |>
  filter(month == current_month) |>
  mutate(full_label = page_url, label = page_url)

site_dropdown_barh(
  top_pages_plot,
  label_col = "label", value_col = "page_views",
  value_name = "Page views",
  title_prefix = paste0("Top Pages by Page Views (", current_month_str, ")")
)
```

## Row {height=480px}

### Top Referrers {width=50%}

```{r}
top_ref_plot <- top_referrers |>
  filter(month == current_month) |>
  filter(!is.na(referrer_url), referrer_url != "", referrer_url != "(unknown)") |>
  mutate(full_label = referrer_url, label = referrer_url)

site_dropdown_barh(
  top_ref_plot,
  label_col = "label", value_col = "page_views",
  value_name = "Page views",
  title_prefix = paste0("Top Referrers (", current_month_str, ")"),
  top_n = 12,
  pre_aggregate = TRUE,
  include_all_sites = TRUE,
  default_site = "all_sites"
)
```

### Operating System Share {width=50%}

```{r}
os_plot <- by_os |>
  filter(month == current_month) |>
  mutate(label = os, full_label = os)

site_dropdown_barh(
  os_plot,
  label_col = "label", value_col = "page_views",
  value_name = "Page views",
  title_prefix = paste0("Page Views by Operating System (", current_month_str, ")"),
  top_n = 10,
  pre_aggregate = TRUE,
  include_all_sites = TRUE,
  default_site = "all_sites"
)
```

## Row {height=440px}

### Top Locations by Page Views

```{r}
geo_plot <- by_geo |>
  filter(month == current_month)
if (!"region" %in% names(geo_plot)) geo_plot$region <- NA_character_
if (!"country" %in% names(geo_plot)) geo_plot$country <- NA_character_
geo_plot <- geo_plot |>
  mutate(
    region = ifelse(is.na(region) | region == "", NA_character_, region),
    country = ifelse(is.na(country) | country == "", "(unknown)", country)
  ) |>
  # Keep all traffic: when the province/state is unknown, fall back to the
  # country as the location rather than dropping the row. This avoids
  # understating countries whose visits are mostly region-less (e.g. China).
  mutate(
    label = ifelse(is.na(region), country, paste0(region, ", ", country)),
    full_label = label
  ) |>
  filter(label != "(unknown)")

site_dropdown_barh(
  geo_plot,
  label_col = "label", value_col = "page_views",
  value_name = "Page views",
  title_prefix = paste0("Top Locations by Page Views (", current_month_str, ")"),
  top_n = 12, pre_aggregate = TRUE,
  include_all_sites = TRUE,
  default_site = "all_sites"
)
```

# BC Stats Product Use {scrolling="true"}

```{r govstats-flags, include=FALSE}
has_assets <- !is.null(asset_daily) && nrow(asset_daily) > 0
has_search <- !is.null(search_terms) && nrow(search_terms) > 0
has_google <- !is.null(google_queries) && nrow(google_queries) > 0

# Asset downloads are dated, so report current-month totals with a MoM scaffold.
total_downloads <- if (has_assets) month_total(asset_daily_by_month, "downloads", current_month) else NA_real_
previous_downloads <- if (has_assets) month_total(asset_daily_by_month, "downloads", previous_month) else NA_real_
downloads_delta <- if (has_assets) {
  delta_caption(total_downloads, previous_downloads, previous_month_str)
} else ""

# Search terms and Google queries are now month-partitioned too.
total_searches  <- if (has_search) month_total(search_terms_by_month, "searches", current_month) else NA_real_
previous_searches <- if (has_search) month_total(search_terms_by_month, "searches", previous_month) else NA_real_
searches_delta  <- if (has_search) delta_caption(total_searches, previous_searches, previous_month_str) else ""
total_g_clicks  <- if (has_google) month_total(google_queries_by_month, "clicks", current_month) else NA_real_
previous_g_clicks <- if (has_google) month_total(google_queries_by_month, "clicks", previous_month) else NA_real_
g_clicks_delta  <- if (has_google) delta_caption(total_g_clicks, previous_g_clicks, previous_month_str) else ""
total_g_impress <- if (has_google) month_total(google_queries_by_month, "impressions", current_month) else NA_real_
previous_g_impress <- if (has_google) month_total(google_queries_by_month, "impressions", previous_month) else NA_real_
g_impress_delta <- if (has_google) delta_caption(total_g_impress, previous_g_impress, previous_month_str) else ""
```

Asset and product download activity, on-site search, and Google Search
performance for the **BC Stats** property (the CMS Lite site,
www2.gov.bc.ca/gov/content/data/statistics).

## Row {height=210px}

::: {.valuebox color="primary" title="Asset Downloads in `r current_month_str``r downloads_delta`"}
`r comma(total_downloads)`
:::

::: {.valuebox color="info" title="Site Searches in `r current_month_str``r searches_delta`"}
`r comma(total_searches)`
:::

::: {.valuebox color="success" title="Google Clicks in `r current_month_str``r g_clicks_delta`"}
`r comma(total_g_clicks)`
:::

::: {.valuebox color="secondary" title="Google Impressions in `r current_month_str``r g_impress_delta`"}
`r comma(total_g_impress)`
:::

## Row {height=500px}

### Daily Asset Downloads {width=45%}

```{r}
if (has_assets) {
  d <- asset_daily |>
    filter(month == current_month) |>
    arrange(date)

  plot_ly(
    d,
    x = ~date, y = ~downloads, type = "scatter", mode = "lines",
    line = list(color = "#003366", width = 2),
    hovertemplate = "<b>%{x|%b %d, %Y}</b><br>Downloads: %{y:,}<extra></extra>"
  ) |>
    layout(
      title = list(text = paste0("<b>Daily Asset Downloads (", current_month_str, ")</b>"),
                   font = modifyList(bc_font, list(size = 15, color = "#003366"))),
      xaxis = list(title = "", gridcolor = "#e8ecf0", tickformat = "%b %d",
                   tickfont = modifyList(bc_font, list(size = 10, color = "#2d2d2d"))),
      yaxis = list(title = "", gridcolor = "#e8ecf0", automargin = TRUE,
                   tickfont = modifyList(bc_font, list(size = 10, color = "#5c6b7a"))),
      plot_bgcolor = "#ffffff", paper_bgcolor = "#ffffff",
      margin = list(l = 10, r = 20, t = 50, b = 30)
    ) |>
    config(
      displaylogo = plotly_config$displaylogo,
      modeBarButtonsToRemove = plotly_config$modeBarButtonsToRemove,
      responsive = plotly_config$responsive
    )
} else {
  plot_ly() |>
    add_annotations(text = "No asset download data available.", x = 0.5, y = 0.5,
                    xref = "paper", yref = "paper", showarrow = FALSE,
                    font = modifyList(bc_font, list(size = 13, color = "#5c6b7a"))) |>
    layout(xaxis = list(visible = FALSE), yaxis = list(visible = FALSE))
}
```

### Top Downloaded Assets {width=55%}

```{r}
if (has_assets && !is.null(top_assets)) {
  d <- top_assets |>
    filter(month == current_month) |>
    mutate(
      fname = ifelse(is.na(asset_file) | asset_file == "", basename(asset_url), asset_file),
      full_label = coalesce(asset_url, fname),
      label = shorten_url(coalesce(asset_url, fname))
    ) |>
    arrange(desc(downloads)) |>
    slice_head(n = 15)

  site_dropdown_barh(
    d,
    label_col = "label", value_col = "downloads",
    value_name = "Downloads",
    title_prefix = paste0("Top Downloaded Assets (", current_month_str, ")"),
    top_n = 15, show_dropdown = FALSE
  )
} else {
  plot_ly() |>
    add_annotations(text = "No asset data available.", x = 0.5, y = 0.5,
                    xref = "paper", yref = "paper", showarrow = FALSE,
                    font = modifyList(bc_font, list(size = 13, color = "#5c6b7a"))) |>
    layout(xaxis = list(visible = FALSE), yaxis = list(visible = FALSE))
}
```

## Row {height=520px}

### Top Site Search Terms {width=45%}

```{r}
if (has_search) {
  d <- search_terms |>
    filter(month == current_month) |>
    arrange(desc(searches)) |>
    slice_head(n = 15)

  site_dropdown_barh(
    d,
    label_col = "search_term", value_col = "searches",
    value_name = "Searches",
    title_prefix = paste0("Top On-Site Search Terms (", current_month_str, ")"),
    top_n = 15, show_dropdown = FALSE
  )
} else {
  plot_ly() |>
    add_annotations(text = "No search data available.", x = 0.5, y = 0.5,
                    xref = "paper", yref = "paper", showarrow = FALSE,
                    font = modifyList(bc_font, list(size = 13, color = "#5c6b7a"))) |>
    layout(xaxis = list(visible = FALSE), yaxis = list(visible = FALSE))
}
```

### Top 10 Google Search Queries {width=55%}

```{r}
# Column	Meaning
# Query:	The search term a user typed into Google
# Page:	The specific URL on your site that appeared in Google's results for that query
# Clicks:	How many times users clicked that URL from Google results
# Impressions:	How many times that URL appeared in Google results for that query
# CTR:	Click-through rate = Clicks ÷ Impressions
if (has_google) {
  google_tbl <- google_queries |>
    filter(month == current_month) |>
    arrange(desc(clicks)) |>
    slice_head(n = 10) |>
    transmute(
      Query = query,
      Page = page,
      Clicks = clicks,
      Impressions = impressions,
      CTR = percent(ctr, accuracy = 0.1)
    )

  datatable(
    google_tbl,
    options = list(pageLength = 10, dom = "t", scrollX = TRUE, order = list(list(2, "desc"))),
    rownames = FALSE
  )
} else {
  cat("No Google Search data available.")
}
```

# About

### About This Dashboard

**Maintainer / Contact**: Data Science Team

**Data Source**: Web traffic report exports for three BC Stats web properties:
BC Stats, Anti-Racism Data Act, and Student Outcomes. These reports are retrieved
from the shared GDX S3 folder by `R/gdx-01-fetch-s3.R` and summarized by
`R/gdx-02-analyze.R`.

**Coverage**: Reporting period `r date_range_str`. The dashboard tracks usage
patterns for three BC Stats web properties. Value boxes report the latest
month's totals.

- **BC Stats** — CMS Lite content on gov.bc.ca, including
  `www2.gov.bc.ca/gov/content/data/statistics` and related sub-themes
- **Anti-Racism Data Act** — WordPress site at `antiracism.gov.bc.ca`
- **Student Outcomes** — WordPress site at `outcomes.bcstats.gov.bc.ca`

**Reports per property**: Each property includes daily page views by URL, daily
clicks by target URL, daily referring URLs, daily platform/operating system
counts, and daily counts by province and country.

The **BC Stats** property also includes additional product-use reporting:
asset/product download counts, on-site search terms, and Google Search query
performance. These outputs are summarized in the **BC Stats Product Use** tab.

**Month-over-month change**: Value boxes show the latest month's totals.
Percentage change compared with the previous month appears automatically once
more than one month of data is available. 

**How we build this**: Created with [Quarto Dashboards](https://quarto.org/docs/dashboards/)
in R, using `dplyr`, `ggplot2`, and `plotly`. The data extraction and rendering
code is open source.

**Source Code**: Find the source code on our [GitHub Repository](https://github.com/bcgov/bcstats-webtraffic-monitoring).
